Report: Complex Support Vector Detector for Large MIMO System

### 2015-10-11 Report Aug 5 2015/Report Aug 2015.tex
report  revised until P28

The sufficient and necessary conditions such that a solution $\mathbf{w}$ of the constrained optimization problem in (\ref{primal optimization problem}) satisfies, are called Karush-Kuhn-Tucker (KKT) conditions. Here we briefly introduce how the dual objective problem is derived from KKT conditions.

@@

 L(\mathbf{x}, \bar{a}_{i})\geq L(\bar{\mathbf{x}}, \bar{a}_{i})\geq L(\bar{\mathbf{w}}, a_{i})

@@

\frac{\partial L}{\partial b}=\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha}_{i})=0\\

@@

In order to satisfy the second inequality in (\ref{KKT inequalities}), (\ref{original KKT condition2}) and  (\ref{original KKT condition3}) have to hold. Satisfying the condition (\ref{original KKT condition2}) is equivalent to find the maximum of $L(\bar{\mathbf{w}}, a_{i})$, notice $\theta(\alpha_{i}, \hat{\alpha}_{i})$ is equivalent to $L(\bar{\mathbf{w}}, a_{i})$ in (\ref{KKT inequalities}), thus yield the dual optimization problem which is given by 

@@

Condition in (\ref{original KKT condition3}) is called KKT complementary condition, the value of $\sum_{i=1}^{L}\bar{a}_{i}c_{i}(\bar{\mathbf{w}})$ can monitor how close the solution is to the global optimum. Thus it can be used as a stopping criterion. In the constraint optimization problem of (\ref{lagrange duality1}), the KKT complementary conditions are given by 
\begin{IEEEeqnarray}[\relax]{l}
\left\{\begin{array}{cc}
\alpha_{i}(y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b-\epsilon-\xi_{i})=0, i=1,2\cdots L\\
\hat{\alpha}_{i}(\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i}-\epsilon-\hat{\xi}_{i})=0, i=1,2\cdots L
\end{array}\right. 
\label{KKT complimentary}
\end{IEEEeqnarray}

@@

\section{System Model}\label{system model}
  Consider a uncoded complex large MIMO uplink spatial multiplexing (SM) system with $N_{t}$ users, where each is equipped with transmit antenna. The number of receive antennas at the Base Station (BS) is $N_{r}$, $N_{r}\geq N_{t}$. Typically large MIMO systems have hundreds of antennas at the BS, as shown in Fig {\ref{large MIMO uplink model}}.
  \begin{figure}[htb]
  \centering
  \def\svgwidth{\columnwidth}
  %\includegraphics[scale=•]{•}
  \input{largeMIMOuplink.pdf_tex}
  \caption{Large MIMO uplink system }
  \label{large MIMO uplink model}
  \end{figure}

@@

The task of a MIMO detector is to estimate the transmit symbol vector $\mathbf{s}$, based on the knowledge of receive symbol vector $\mathbf{y}$ and channel matrix $\mathbf{H}$.

\section{Dual Channel Complex Support Vector detection for Large MIMO system}\label{dual channel CSVR}
 Based on discrete time model of large MIMO uplink system in (\ref{discrete time MIMO system}), in our  regression model, the training data sample at detector is $(\mathbf{h}_{1}, y_{1})(\mathbf{h}_{2}, y_{2}), \ldots, (\mathbf{h}_{N_{r}}, y_{N_{r}})$, where $\mathbf{h}_{i}$ denotes $i$th row of channel propagation matrix $\mathbf{H}$, this yields a regression task without offset $b$:  
 \begin{eqnarray}
 y_{i}=f_{true}(\mathbf{h}_{i})+n,\\
 \label{regression part1a}
 f_{true}(\mathbf{h}_{i})=\mathbf{h}_{i}\mathbf{s},\\
 \label{regression part1b}
 \end{eqnarray}
 where $f_{true}()$ denotes the underlying true function, $n$ denotes additive noise.
In this regression problem, receive symbol $y$ is the output data, $\mathbf{h}$ is input data sample, transmitted symbol vector $s$ is regression coefficients. Because the large MIMO system we consider here is complex, we employ complex support vector regression (CSVR) without offset term $b$. As shown in section \ref{Introduce epsilon SVR}, in order to derive Lagrange duality optimization formula, partial derivatives of objective function with respect to $\mathbf{w}$ and $\xi$ are needed to be calculated, in CSVR, that means take partial derivatives to risk functions which are defined in complex domain. Recently mathematical results of Wirtinger's calculus in Reproducing Kernel Hilbert Space (RKHS) is employed to solve this problem\cite{bouboulis2011extension}. First we generalize our regression model by complex RKHS, 
Let $<,>_{H}$ denotes inner product operation in real RKHS. $<,>_{\mathbb{H}}$ denotes inner products operation in complex RKHS. Assume $\mathbf{x}$, $\mathbf{y}$, $\mathbf{z}$, $j$, $k$ $\in \mathbb{C}$, complex Hilbert space has the following properties 
\newtheorem{Lemma}{Lemma}
\newtheorem{Property}{Property}
\begin{Property}
 $<\mathbf{x},\mathbf{y}>_{\mathbb{H}}=<\overline{\mathbf{y},\mathbf{x}}>_{\mathbb{H}}$
\label{CHSProperty1}
\end{Property}

\begin{Property}
$<j\mathbf{x}+k\mathbf{y},\mathbf{z}>_{\mathbb{H}}=j<\mathbf{x},\mathbf{z}>_{\mathbb{H}}+k<\mathbf{y},\mathbf{z}>_{\mathbb{H}}$
\label{CHSProperty2}
\end{Property}

\begin{Property}
$<\mathbf{z}, j\mathbf{x}+k\mathbf{y}>=\bar{j}<\mathbf{z},\mathbf{x}>_{\mathbb{H}}+\bar{k}<\mathbf{z}, \mathbf{y}>_{\mathbb{H}}$
\label{CHSProperty3}
\end{Property}

\begin{Lemma}
$\mathbf{h}_{i}\mathbf{s}\in <\mathbf{h}_{i},\mathbf{s}^{*}>_{\mathbb{H}}$
\end{Lemma}

\begin{proof}
Assume $\mathbf{a}$, $\mathbf{b}$ $\in \mathbb{R}^{v}$, it can be easily proved  
\begin{equation}
\mathbf{a}^{T}\mathbf{b} \in <\mathbf{a}, \mathbf{b}>_{H},
\label{CHSequation1}
\end{equation}
 From Property \ref{CHSProperty1} and Property \ref{CHSProperty3}, it is obvious 
\begin{equation}
<\mathbf{g},\mathbf{h}>_{\mathbb{H}}=<\mathbf{g}^{r},\mathbf{h}^{r}>_{H}+<\mathbf{g}^{i},\mathbf{h}^{i}>_{H}+i(<\mathbf{g}^{i},\mathbf{h}^{r}>_{H}-<\mathbf{g}^{r},\mathbf{h}^{i}>_{H})
\label{CHSProperty4}
\end{equation}
where $\mathbf{g}$,$\mathbf{h}$ $\in \mathbb{C}^{v}$, and $\mathbf{g}=\mathbf{g}^{r}+i\mathbf{g}^{i}$, $\mathbf{h}=\mathbf{h}^{r}+i\mathbf{h}^{i}$. Therefore, 
\begin{eqnarray}
\nonumber
<\mathbf{h}, \mathbf{s}^{*}>_{\mathbb{H}}&=&<\mathbf{h}^{r},  (\mathbf{s}^{*})^{r}>_{H}+<\mathbf{h}^{i},  (\mathbf{s}^{*})^{i}>_{H}+i(<\mathbf{h}^{i},  (\mathbf{s}^{*})^{r}>_{H}-<\mathbf{h}^{r},  (\mathbf{s}^{*})^{i}>_{H})\\
&=&<\mathbf{h}^{r}, \mathbf{s}^{r}>_{H}-<\mathbf{h}^{i}, \mathbf{s}^{i}>_{H}+i(<\mathbf{h}^{i}, \mathbf{s}^{r}>_{H}+<\mathbf{h}^{r}, \mathbf{s}^{i}>_{H}),
\label{CHSequation2}
\end{eqnarray}
\mathbf{h}\mathbf{s}=\mathbf{h}^{r}\mathbf{s}^{r}-\mathbf{h}^{i}\mathbf{s}^{i}+i(\mathbf{h}^{i}\mathbf{s}^{r}+\mathbf{h}^{r}\mathbf{s}^{i}),
\label{CHSequation3}
Because of (\ref{CHSequation1}), (\ref{CHSequation2}) and (\ref{CHSequation3}), $\mathbf{h}_{i}\mathbf{s}\in <\mathbf{h}_{i},\mathbf{s}^{*}>_{\mathbb{H}}$.

@@

represent $\mathbf{s}^{*}$ by $\mathbf{w}$, The general regularized risk function of large MIMO detection in complex RKHS can be formulated:
\begin{eqnarray}

@@

minimize \quad \frac{1}{2}||w||_{\mathbb{H}}^{2}+C\sum_{k=1}^{N_{r}}[(R(\xi^{r}_{k})+R(\hat{\xi}^{r}_{k})+R(\xi^{i}_{k})+R(\hat{\xi}^{i}_{k}))]\\

@@

Re(y_{k}-<\mathbf{h}_{k},\mathbf{w}>_{\mathbb{H}})\leq \epsilon+\xi^{r}_{k}\\
Re(<\mathbf{h}_{k},\mathbf{w}>_{\mathbb{H}}-y_{k})\leq \epsilon+\hat{\xi}^{r}_{k}\\
Im(y_{k}-<\mathbf{h}_{k},\mathbf{w}>_{\mathbb{H}})\leq \epsilon+\xi^{i}_{k}\\
Im(<\mathbf{h}_{k},\mathbf{w}>_{\mathbb{H}}-y_{k})\leq \epsilon+\hat{\xi}^{i}_{k}\\
\xi^{r}, \hat{\xi}^{r},\xi^{i},\hat{\xi}^{i}\geq 0\\

@@

\end{eqnarray}
where $Re()$ and $Im()$ denote real part and imaginary part of a complex variable, restrictions are set to real and imaginary part of regression function separately. Let $\mathbf{K}=\mathbf{H}\mathbf{H}^{H}$ denotes the kernel function, $\mathbf{K}=\mathbf{K}^{r}+i\mathbf{K}^{i}$, $\mathbf{K}^{r}$ and $\mathbf{K}^{i}$ denote matrix of corresponding real part and imaginary part. Similar to the Lagrange duality rational in section \ref{section lagrange duality}, Lagrange function is formulated for (\ref{complex objective function1}) 

@@

\theta =
\frac{1}{2}||w||_{\mathbb{H}}^{2}+C\sum_{k=1}^{N_{r}}[(R(\xi^{r}_{k})+R(\hat{\xi}^{r}_{k})+R(\xi^{i}_{k})+R(\hat{\xi}^{i}_{k}))]- \sum_{k=1}^{N_{r}}(\eta_{i}\xi^{r}_{k}+\hat{\eta}_{k}\hat{\xi}^{r}_{k}+\tau_{k}\xi^{i}_{k}+\hat{\tau}_{k}\hat{\xi}^{i}_{k})\\

@@

-\sum_{k=1}^{N_{r}}\alpha_{k}(\epsilon+\xi^{r}_{k}-Re(y_{k})+Re(<\mathbf{h}_{k},\mathbf{w}>_{\mathbb{H}}))
-\sum_{k=1}^{N_{r}}\hat{\alpha}_{k}(\epsilon+\hat{\xi}^{r}_{k}+Re(y_{k})-Re(<\mathbf{h}_{k},\mathbf{w}>_{\mathbb{H}}))\\
-\sum_{k=1}^{N_{r}}\beta_{k}(\epsilon+\xi^{i}_{k}-Im(y_{k})+Im(<\mathbf{h}_{k},\mathbf{w}>_{\mathbb{H}}))-\sum_{k=1}^{N_{r}}\hat{\beta}_{k}(\epsilon+\hat{\xi}^{i}_{k}+Im(y_{k})-Im(<\mathbf{h}_{k},\mathbf{w}>_{\mathbb{H}}))\\

@@

\eta, \hat{\eta}, \tau, \hat{\tau} \alpha, \hat{\alpha}, \beta, \hat{\beta}\geq 0\\
\xi^{r}, \hat{\xi}^{r}, \xi^{i}, \hat{\xi}^{i} \geq  0

@@

with Wirtinger's calculus applied to RKHS described in \cite{bouboulis2011extension}, The partial derivatives of $\theta$ respect to $\mathbf{w}$, which is define at complex domain, as well as the real variables $\xi^{r}$, $\hat{\xi}^{r}$, $\xi^{i}$ and $\hat{\xi}^{i}$ can be deduced 

@@

\frac{\partial \Theta}{\partial \mathbf{w}^{*}}=\frac{1}{2}\mathbf{w}-\frac{1}{2}\sum_{k=1}^{N_{r}}\alpha_{k}\mathbf{h}_{k}+\frac{1}{2}\sum_{k=1}^{N_{r}}\hat{\alpha}_{k}\mathbf{h}_{k}+\frac{i}{2}(\sum_{k=1}^{N_{r}}\beta_{k}\mathbf{h}_{k}-\sum_{k=1}^{N_{r}}\hat{\beta}_{k}\mathbf{h}_{k})=0\\
\Rightarrow \mathbf{w}=\sum_{k=1}^{N_{r}}(\alpha_{k}-\hat{\alpha}_{k})\mathbf{h}_{k}-i\sum_{k=1}^{N_{r}}(\beta_{k}-\hat{\beta}_{k})\mathbf{h}_{k}\\
\frac{\partial \Theta}{\partial \xi^{r}_{k}}=CR^{'}(\xi^{r}_{k})-\eta_{k}-\alpha_{k}=0\Rightarrow \eta_{k}=CR^{'}(\xi^{r}_{k})-\alpha_{k}\\
\frac{\partial \Theta}{\partial \hat{\xi}^{r}_{k}}=CR^{'}(\hat{\xi}^{r}_{k})-\hat{\eta}_{k}-\hat{\alpha}_{k}=0\Rightarrow \hat{\eta}_{k}=CR^{'}(\hat{\xi}^{r}_{k})-\hat{\alpha}_{k}\\
\frac{\partial \Theta}{\partial \xi^{i}_{k}}=CR^{'}(\xi^{i}_{k})-\tau_{k}-\beta_{k}=0\Rightarrow \tau_{k}=CR^{'}(\xi^{i}_{k})-\beta_{k}\\
\frac{\partial \Theta}{\partial \hat{\xi}^{i}_{k}}=CR^{'}(\hat{\xi}^{i}_{k})-\hat{\eta}_{k}-\hat{\beta}_{k}=0\Rightarrow \hat{\eta}_{k}=CR^{'}(\hat{\xi}^{i}_{k})-\hat{\beta}_{k}\\

>>>>

The sufficient and necessary conditions such that a solution $\mathbf{w}$ of the constrained optimization problem in (\ref{primal optimization problem}) satisfies, are called Karush-Kuhn-Tucker (KKT) conditions. Here we elaborate a little further about how the dual objective problem is derived from KKT conditions.

@@

 L(\mathbf{w}, \bar{a}_{i})\geq L(\bar{\mathbf{w}}, \bar{a}_{i})\geq L(\bar{\mathbf{w}}, a_{i})

@@

\frac{\partial L}{\partial b}=\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha}_{i})=0\\\nonumber

@@

In order to satisfy the second inequality in (\ref{KKT inequalities}), (\ref{original KKT condition2}) and  (\ref{original KKT condition3}) have to hold. Condition (\ref{original KKT condition2}) is satisfied when the maximum of $L(\bar{\mathbf{w}}, a_{i})$ is found, notice $\theta(\alpha_{i}, \hat{\alpha}_{i})$ is equivalent to $L(\bar{\mathbf{w}}, a_{i})$ in (\ref{KKT inequalities}), thus yielding the dual optimization problem, which is given by 

@@

Condition in (\ref{original KKT condition3}) is called KKT complementary condition, the value of $\sum_{i=1}^{L}\bar{a}_{i}c_{i}(\bar{\mathbf{w}})$ can be used to monitor how close the solution is to the global optimum. Thus it can be used as a stopping criterion. In the constraint optimization problem of (\ref{lagrange duality1}), the KKT complementary conditions are given by 
\begin{IEEEeqnarray}[\relax]{l}
\left\{\begin{array}{cc}
\alpha_{i}(y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b-\epsilon-\xi_{i})=0, i=1,2\cdots L\\
\hat{\alpha}_{i}(\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i}-\epsilon-\hat{\xi}_{i})=0, i=1,2\cdots L
\end{array}\right. 
\label{KKT complimentary}
\end{IEEEeqnarray}

@@

\section{Dual Channel Complex Support Vector detection for Large MIMO system}\label{dual channel CSVR}
\subsection{System Model}\label{system model}
  Consider a uncoded complex large MIMO uplink spatial multiplexing (SM) system with $N_{t}$ users, where each is equipped with transmit antenna. The number of receive antennas at the Base Station (BS) is $N_{r}$, $N_{r}\geq N_{t}$. Typically large MIMO systems have hundreds of antennas at the BS, as shown in Fig {\ref{large MIMO uplink model}}.
  \begin{figure}[htb]
  \centering
  \def\svgwidth{\columnwidth}
  %\includegraphics[scale=•]{•}
  \input{largeMIMOuplink.pdf_tex}
  \caption{Large MIMO uplink system }
  \label{large MIMO uplink model}
  \end{figure}

@@

The task of a MIMO detector is to estimate the transmit symbol vector $\mathbf{s}$, based on the knowledge of receive symbol vector $\mathbf{y}$ and channel matrix $\mathbf{H}$.
\subsection{Complex Regression Model}
 Based on the discrete time model of the large MIMO uplink system of (\ref{discrete time MIMO system}), our regression model is set such that the training data samples at the detector are $(\mathbf{h}_{1}, y_{1})(\mathbf{h}_{2}, y_{2}), \ldots, (\mathbf{h}_{N_{r}}, y_{N_{r}})$, where $\mathbf{h}_{i}$ denotes $i$th row of matrix $\mathbf{H}$. This yields a regression task without offset $b$ in (\ref{equation1}) :  
 \begin{IEEEeqnarray}[\relax]{l}
 y_{i}=f_{true}(\mathbf{h}_{i})+n_{i}, i=1,2\ldots L\\
 \label{regression part1a}
 f_{true}(\mathbf{h}_{i})=\mathbf{h}_{i}\cdot\mathbf{s}, i=1,2,\ldots, L\\
 \label{regression part1b}
 \end{IEEEeqnarray}
 where $f_{true}()$ denotes the underlying true regression function, $n_{i}$ denotes discrete sample of additive noise.
In this regression problem, received symbols $y_{i}$ are the output data, $\mathbf{h}_{i}$ are the input data samples, transmitted symbol vector $\mathbf{s}$ contains the regression coefficients. We employ complex support vector regression (CSVR) without offset term $b$, in order to deal with the complex large MIMO systems. As shown in section \ref{Introduce epsilon SVR}, As shown in (\ref{original KKT condition1}) the first KKT condition is satisfied by finding the saddle point $\bar{\mathbf{w}}$ by taking paritial derivatives of $L(\mathbf{w},a_{i})$ with respect to $\mathbf{w}$. Mathematical results of Wirtinger's calculus in Reproducing Kernel Hilbert Space (RKHS) are employed to calculate partial derivatives of Lagrangian function of CSVR in complex manner\cite{bouboulis2011extension}. First we generalize our regression model by complex RKHS, 
Define a real RKHS $\mathcal{H}$, $<,>_{\mathcal{H}}$ denotes the corresponding inner product in $\mathcal{H}$. define complex RKHS $\mathbb{H}=\{f=f^{r}+\imath f^{i}, f^{r}, f^{i}\in \mathcal{H}\}$, $<,>_{\mathbb{H}}$ denotes the corresponding inner products in $\mathbb{H}$. Assume $\mathbf{x}$, $\mathbf{y}$, $\mathbf{z}$, $\mu$, $\chi$ $\in \mathbb{C}$, complex Hilbert space has the following properties 
\newtheorem{Lemma}{Lemma}
\newtheorem{Property}{Property}
\begin{Property}
 $<\mathbf{x},\mathbf{y}>_{\mathbb{H}}=(<{\mathbf{y},\mathbf{x}}>_{\mathbb{H}})^{*}$
\label{CHSProperty1}
\end{Property}

\begin{Property}
$<\mu\mathbf{x}+\chi\mathbf{y},\mathbf{z}>_{\mathbb{H}}=\mu<\mathbf{x},\mathbf{z}>_{\mathbb{H}}+\chi<\mathbf{y},\mathbf{z}>_{\mathbb{H}}$
\label{CHSProperty2}
\end{Property}

\begin{Property}
$<\mathbf{z}, \mu\mathbf{x}+\chi\mathbf{y}>_{\mathbb{H}}=\mu^{*}<\mathbf{z},\mathbf{x}>_{\mathbb{H}}+\chi^{*}<\mathbf{z}, \mathbf{y}>_{\mathbb{H}}$
\label{CHSProperty3}
\end{Property}

\begin{Lemma}
Assume $\mathbf{a}$, $\mathbf{b}$ $\in \mathbb{R}^{V}$, define a real RKHS $\mathcal{H}$ that satisfy $<\mathbf{a}, \mathbf{b}>_{\mathcal{H}}=\mathbf{a}^{T}\mathbf{b}$. For the corresponding complex RKHS $\mathbb{H}=\{f=f^{r}+\imath f^{i}, f^{r}, f^{i}\in \mathcal{H}\}$,
$<\mathbf{m},\mathbf{l}^{*}>_{\mathbb{H}}=\mathbf{m}\cdot \mathbf{l}$
\end{Lemma}

\begin{proof} 
$\mathbf{g}$,$\mathbf{h}$ $\in \mathbb{C}^{V}$, and $\mathbf{g}=\Re{(\mathbf{g})}+\imath\Im{(\mathbf{g})}$, $\mathbf{h}=\Re{(\mathbf{h})}+\imath\Im{(\mathbf{h})}$. From Property \ref{CHSProperty1} and Property \ref{CHSProperty3},  
\begin{IEEEeqnarray}[\relax]{l}
<\mathbf{g},\mathbf{h}>_{\mathbb{H}}=<\Re{(g)}+\imath\Im{(g)}, \Re{(h)}+\imath\Im{(h)}>_{\mathbb{H}}
\label{CHSProperty4 inter1}
\end{IEEEeqnarray}
According to Property \ref{CHSProperty2}, (\ref{CHSProperty4 inter1}) can be rewritten as 
\begin{equation}
<\mathbf{g},\mathbf{h}>_{\mathbb{H}}=<\Re{(\mathbf{g})}, \Re{(\mathbf{h})}+\imath\Im{(\mathbf{h})}>_{\mathbb{H}}+\imath <\Im{(\mathbf{g})}, \Re{(\mathbf{h})}+\imath\Im{(\mathbf{h})}>_{\mathbb{H}},
\label{CHSProperty4 inter2}
\end{equation}
According to Property \ref{CHSProperty3}
\begin{IEEEeqnarray}[\relax]{l}
\nonumber
<\mathbf{g},\mathbf{h}>_{\mathbb{H}}=<\Re{(\mathbf{g})}, \Re{(\mathbf{h})}>_{\mathbb{H}}-\imath <\Re{(\mathbf{g})}, \Im{(\mathbf{h})}>_{\mathbb{H}}+\imath (<\Im{(\mathbf{g})}, \Re{(\mathbf{h})}>_{\mathbb{H}}-
\imath <\Im{(\mathbf{g})}, \\ \nonumber  \Im{(\mathbf{h})}>_{\mathbb{H}})
=<\Re{(\mathbf{g})},\Re{(\mathbf{h})}>_{\mathbb{H}}+<\Im{(\mathbf{g})},\Im{(\mathbf{h})}>_{\mathbb{H}}+\imath [<\Im{(\mathbf{g})},\Re{(\mathbf{h})}>_{\mathbb{H}}-<\Re{(\mathbf{g})},\\ \Im{(\mathbf{h})}>_{\mathbb{H}}]
\label{CHSProperty4 inter2}
\end{IEEEeqnarray}
Because $<\mathbf{f}_{1}, \mathbf{f}_{2}>_{\mathbb{H}}=<\mathbf{f}_{1}, \mathbf{f}_{2}>_{\mathcal{H}}=\mathbf{f}^{T}_{1}\cdot \mathbf{f}_{2}$ if $\mathbf{f}_{1}, \mathbf{f}_{2}\in \mathcal{H}$, thus (\ref{CHSProperty4 inter2}) can be rewritten as 
\begin{IEEEeqnarray}[\relax]{l}
\nonumber
<\mathbf{g},\mathbf{h}>_{\mathbb{H}}=<\Re{(\mathbf{g})},\Re{(\mathbf{h})}>_{\mathcal{H}}+<\Im{(\mathbf{g})},\Im{(\mathbf{h})}>_{\mathcal{H}}+\imath [<\Im{(\mathbf{g})},\Re{(\mathbf{h})}>_{\mathcal{H}}-<\Re{(\mathbf{g})}, \Im{(\mathbf{h})}>_{\mathcal{H}}]=\\
\Re{(\mathbf{g})}^{T}\cdot \Re{(\mathbf{h})}+\Im{(\mathbf{g})}^{T}\cdot \Im{(\mathbf{h})}+\imath [\Im{(\mathbf{g})}^{T}\cdot  \Re{(\mathbf{h})}-\Re{(\mathbf{g})}^{T}\cdot \Im{(\mathbf{h})}]=\mathbf{g}\cdot \mathbf{h}^{*}
\label{CHSequation2}
\end{IEEEeqnarray}

Therefore $<\mathbf{m},\mathbf{l}>_{\mathbb{H}}=\mathbf{m}\cdot \mathbf{l}$.

@@

Therefore we have $<\mathbf{h}_{i}, \mathbf{s}^{*}>_{\mathbb{H}}=\mathbf{h}_{i}\cdot \mathbf{s}$, 
For sake of simplicity we define $\mathbf{s}^{*}=\mathbf{w}$. Based on the same principle in the real case presented in (\ref{Introduce epsilon SVR}), the general regularized risk function of large MIMO detection in complex RKHS $\mathbb{H}$ defined by $<\mathbf{m}, \mathbf{l}>_{\mathbb{H}}=\mathbf{m}^{T}\mathbf{l}$ can be formulated as 

@@

\min_{\mathbf{w}, \xi^{r}_{i}, \hat{\xi}^{r}_{i}, \xi^{i}_{i}, \hat{\xi}^{i}_{i}} \quad \frac{1}{2}||\mathbf{w}||_{\mathbb{H}}^{2}+C\sum_{i=1}^{N_{r}}[(R(\xi^{r}_{i})+R(\hat{\xi}^{r}_{i})+R(\xi^{i}_{i})+R(\hat{\xi}^{i}_{i}))]\\

@@

\Re{(y_{i}-<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})}\leq \epsilon+\xi^{r}_{i}, i=1,2,\ldots, N_{r}\\
\Re{(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-y_{i})}\leq \epsilon+\hat{\xi}^{r}_{i}, i=1,2,\ldots, N_{r}\\
\Im{(y_{i}-<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})}\leq \epsilon+\xi^{i}_{i}, i=1,2,\ldots, N_{r}\\
\Im{(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-y_{i})}\leq \epsilon+\hat{\xi}^{i}_{i}, i=1,2,\ldots, N_{r}\\
\xi^{r}_{i}, \hat{\xi}^{r}_{i},\xi^{i}_{i},\hat{\xi}^{i}_{i}\geq 0, i=1,2,\ldots, N_{r}\\

@@

 Where $\Re{(\cdot)}$ and $\Im{(\cdot)}$ denote real and imaginary part of a complex variable and inequality restrictions are set to real and imaginary part of the regression function separately. Let $\mathbf{K}=\mathbf{H}\mathbf{H}^{H}$ denote the kernel function, $\mathbf{K}=\Re{(\mathbf{K})}+\imath\Im{(\mathbf{K})}$, where $\Re{(\mathbf{K})}$ and $\Im{(\mathbf{K})}$ denote matrices of corresponding real and imaginary parts. Similar to the Lagrange duality rational in section \ref{section lagrange duality}, the Lagrange function associated with (\ref{complex objective function1}) is 

@@

L=
\frac{1}{2}||\mathbf{w}||_{\mathbb{H}}^{2}+C\sum_{i=1}^{N_{r}}[(R(\xi^{r}_{i})+R(\hat{\xi}^{r}_{i})+R(\xi^{i}_{i})+R(\hat{\xi}^{i}_{i}))]- \sum_{i=1}^{N_{r}}(\eta_{i}\xi^{r}_{i}+\hat{\eta}_{i}\hat{\xi}^{r}_{i}+\tau_{i}\xi^{i}_{i}\\\nonumber +\hat{\tau}_{i}\hat{\xi}^{i}_{i})
+\sum_{i=1}^{N_{r}}\alpha_{i}(\Re{(y_{i})}-\Re{(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})}-\epsilon-\xi^{r}_{i})
+\sum_{i=1}^{N_{r}}\hat{\alpha}_{i}(\Re{(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})}-\Re{(y_{i})}-\epsilon-\hat{\xi}^{r}_{i})\\

@@

+\sum_{i=1}^{N_{r}}\beta_{i}(\Im{(y_{i})}-\Im{(<\mathbf{h}_{k},\mathbf{w}>_{\mathbb{H}})}-\epsilon-\xi^{i}_{i})+\sum_{i=1}^{N_{r}}\hat{\beta}_{i}(\Im{(<\mathbf{h}_{k},\mathbf{w}>_{\mathbb{H}})}-\Im{(y_{i})}-\epsilon-\hat{\xi}^{i}_{i})\\

@@

\eta_{i}, \hat{\eta}_{i}, \tau_{i}, \hat{\tau}_{i}, \alpha_{i}, \hat{\alpha}_{i}, \beta_{i}, \hat{\beta}_{i}\geq 0, i=1,2,\ldots, N_{r}\\
\xi^{r}_{i}, \hat{\xi}^{r}_{i}, \xi^{i}_{i}, \hat{\xi}^{i}_{i} \geq  0, i=1,2,\ldots, N_{r}

@@

where $\eta_{i}, \hat{\eta}_{i}, \tau_{i}, \hat{\tau}_{i}, \alpha_{i}, \hat{\alpha}_{i}, \beta_{i}, \hat{\beta}_{i}$ are Lagrange multipliers. In order to calculate the partial derivations of $L$ with respect to $\mathbf{w}$ which is defined in complex domain, the Wirtinger's calculus is exploited\cite{bouboulis2011extension} , Therefore we have   

@@

\frac{\partial L}{\partial \mathbf{w}^{*}}=\frac{1}{2}\mathbf{w}-\frac{1}{2}\sum_{i=1}^{N_{r}}\alpha_{i}\mathbf{h}_{i}+\frac{1}{2}\sum_{i=1}^{N_{r}}\hat{\alpha}_{i}\mathbf{h}_{i}+\frac{\imath}{2}(\sum_{i=1}^{N_{r}}\beta_{i}\mathbf{h}_{i}-\sum_{i=1}^{N_{r}}\hat{\beta}_{i}\mathbf{h}_{i})=0\\
\Rightarrow \mathbf{w}=\sum_{i=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})\mathbf{h}_{i}-\imath\sum_{i=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})\mathbf{h}_{i}\\
\frac{\partial L}{\partial \xi^{r}_{i}}=CR^{'}(\xi^{r}_{i})-\eta_{i}-\alpha_{i}=0\Rightarrow \eta_{i}=CR^{'}(\xi^{r}_{i})-\alpha_{i}\\
\frac{\partial L}{\partial \hat{\xi}^{r}_{i}}=CR^{'}(\hat{\xi}^{r}_{i})-\hat{\eta}_{i}-\hat{\alpha}_{i}=0\Rightarrow \hat{\eta}_{i}=CR^{'}(\hat{\xi}^{r}_{i})-\hat{\alpha}_{i}\\
\frac{\partial L}{\partial \xi^{i}_{i}}=CR^{'}(\xi^{i}_{i})-\tau_{i}-\beta_{i}=0\Rightarrow \tau_{i}=CR^{'}(\xi^{i}_{i})-\beta_{i}\\
\frac{\partial L}{\partial \hat{\xi}^{i}_{i}}=CR^{'}(\hat{\xi}^{i}_{i})-\hat{\tau}_{i}-\hat{\beta}_{i}=0\Rightarrow \hat{\tau}_{i}=CR^{'}(\hat{\xi}^{i}_{i})-\hat{\beta}_{i}\\

\end{array}\right.
\label{complex lagrange duality2}
\end{IEEEeqnarray}
Based on (\ref{complex lagrange duality2}), we have 
\begin{IEEEeqnarray}[\relax]{l}
\nonumber
<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}}=\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})<\mathbf{h}_{i},\mathbf{h}_{j}>_{\mathbb{H}}+i\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})<\mathbf{h}_{i},\mathbf{h}_{j}>_{\mathbb{H}}\\
\nonumber
=\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\mathbf{h}_{i}\mathbf{h}^{H}_{j}+i\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\mathbf{h}_{i}\mathbf{h}^{H}_{j}\\\nonumber
=\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\Re{(\mathbf{K})}_{ij}-\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\Im{(\mathbf{K})}_{ij}+i(\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\Im{(\mathbf{K})}_{ij}+\\ \sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\Re{(\mathbf{K})}_{ij}),
\label{complex duality regression function}
\end{IEEEeqnarray}
